---
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      error = FALSE)
```

```{r, include=FALSE, echo=FALSE}

# # set working directory
# wd <- dirname(rstudioapi::getSourceEditorContext()$path)
# setwd(wd)

```

````{=html}

<style>

/* body */
body {
  font-family: Helvetica;
  font-size: 16pt;
}

/* title */
h1.title {
  font-size: 32pt;
}

/* subtitle */
h2.subtitle {
  font-size: 24pt;
}

/* author */
h4.authur {
  font-size: 16pt;
}

/* for collapsible button */
.col_button {
  margin-top: 5px;
  margin-bottom: 5px; 
  background-color: white;
  color: #333333;
  font-style: italic;
  cursor: pointer;
  width: 100%;
  padding: 5px;
  border: 1px solid;
  border-color: #cccccc;
  text-align: left;
  outline: none;
  font-family: Helvetica;
  font-size: 16pt;
}

/* for collapsible content */
.col_content {
  display: none;
  background-color: #EAECEE;
  padding-top: 5px;
  padding-right: 10px;
  padding-bottom: 5px;
  padding-left: 10px;
}

</style>

````

<!--..........................................................................-->
<hr>

<h1 class="title">Review, Application and Illustration of <br> Statistical Concepts</h1>

<!--..........................................................................-->
<hr>

<h2 class="subtitle">Illustration of the Law of Large Numbers (LLN) and the Central Limit Theorem (CLT)</h2>

<!--..........................................................................-->
<!--<hr>-->

<h4 class="author"><em>by Markus Mößler</em></h4>

<!-- .................................................. -->
<hr>

<span style="text-decoration: underline; font-size: 18pt">Instructions</span><span style="font-size: 18pt">: Input</span>

The *app* below contains an *illustration of the central limit theorem (CLT)*.

Use the *first slider* to change the value of the *sample size* $N$.

Use the *second slider* to change the value of the *probability of success* $p$ for the *Bernoulli Random Variable*.



<!-- .................................................. -->
<hr>

<span style="text-decoration: underline; font-size: 18pt">Explanation</span><span style="font-size: 18pt">: Output</span>

The first plot (*Sampling Distribution of Sample Average*) shows the histogram of the *sample average* of a *Bernoulli Random Variable* with *probability of success* $p$. 

The second plot (*Sampling Distribution of Standardized Sample Average*) shows the histogram of the *standardized sample average* of a *Bernoulli Random Variable* with *probability of success* $p$. 

The standardization follows:

\begin{align}
Z_{\overline{Y}} = \frac{ \overline{Y} - \mu_{\overline{Y}}}{\sigma_{\overline{Y}}}
\end{align}

For more information see Stock and Watson (2020) on page 86ff.



<!-- .................................................. -->
<hr>

<span style="text-decoration: underline; font-size: 20pt">Bernoulli Random Variable</span>

<!-- ## Bernoulli Random Variable -->

<hr>

```{r ill_01, echo=FALSE, warning=FALSE, message=FALSE, include=TRUE}
shinyAppDir(appDir = "./ShinyApplication_01",
            options = list(width = "100%", height = 1000
  )
)
```



<!-- .................................................. -->
<hr>

<span style="text-decoration: underline; font-size: 24pt">Interpretation</span>

<hr>

<span style="text-decoration: underline; font-size: 18pt">Law of Large Numbers (LLN)</span><span style="font-size: 18pt">: Consistency</span>

As the *sample size* $N$ grows the (absolute) frequency of observing a *sample average* $\overline{Y}$ accumulates around the *population mean* $\mu$, i.e.,

\begin{align}
\overline{Y} \xrightarrow{p} \mu_{\overline{Y}}
\end{align}

See Figure 1 above.



<!-- .................................................. -->
<hr>

<span style="text-decoration: underline; font-size: 18pt">Central Limit Theorem (CLT)</span><span style="font-size: 18pt">: Asymptotic Normality</span>

As the *sample size* $N$ grows the (relative) frequency of the observed *standardized sample average* $Z_{\overline{Y}}$ gets closer to the *probability density* of the *standard normal distribution*, i.e., 

\begin{align}
Z_{\overline{Y}} \xrightarrow{d} N\left( \mu_{\overline{Y}}, \sigma^{2}_{\overline{Y}} \right)
\end{align}

See Figure 2 above.





````{=html}

<script>

var coll = document.getElementsByClassName("col_button");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}

</script>

````


